Formal Grammars as Types in Non-Commutative Linear-Non-Linear Type Theory

### 2024-07-10 POPL/paper.tex
down with DOS

The theory of formal languages and parsing is one of the oldest and
most thoroughly developed areas of theoretical computer science. A
prominent topic in the 1950, 60s, and 70s led to a series of remarkable
developments: Chomsky's hierarchy of grammars \cite{chomThreeModels1956}, practical
algorithms for parsing of regular and context-free grammars and
variants \cite{KNUTH1965607,Earley1970}, as well as implementations of practical tools for the
generation of efficient parsers \cite{Johnsonyacc}.

\steven{I don't like the name \theoryname (\theoryabbv). Feel free to play with it though, as
  its set up as a pair of macros}

In this paper, we propose an intuitive and structured generalization of the
theoretical machinery used for parsing. In conjunction with an updated
point-of-view on formal grammars, we provide a domain-specific
language to build and verify parsers.

>>>>

Parsing data from a serialized format is one of the most common tasks
in all of computing. Accordingly, this is a quite well-studied problem
spanning theoretical computer science and linguistics with such
milestones as Chomsky's hierarchy of grammars
\cite{chomThreeModels1956}, practical algorithms for parsing of
regular and context-free grammars and variants
\cite{KNUTH1965607,Earley1970}, as well as implementations of
practical tools for the generation of efficient parsers
\cite{Johnsonyacc}.
%

%% The theory of formal languages and parsing is one of the oldest and
%% most thoroughly developed areas of theoretical computer science. A
%% prominent topic in the 1950, 60s, and 70s led to a series of remarkable
%% developments: 
In this paper, we propose an intuitive and structured generalization of the
theoretical machinery used for parsing. In conjunction with an updated
point-of-view on formal grammars, we provide a domain-specific
language to build and verify parsers.
